%
% File acl2015.tex
%
% Contact: car@ir.hit.edu.cn, gdzhou@suda.edu.cn
%%
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2015}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.


\title{Instructions for ACL-2015 Proceedings}

\author{Shuwei Zhang \\
  {\tt shuweiz@usc.edu} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle

\section{Project Domain \& Goals}

\section{Related Work}

\section{Data}

In order to build a text-based recommendation system, we need to find a dataset that records reviews and rating toward restaurants. Fortunately, Yelp has established a well-organized streamed database \footnote{Yelp Dataset documentation url: \url{https://www.yelp.com/dataset/documentation/main}} that provides reviews and ratings from customers, and the information about the restaurants those reviews are about. In this database, all the data is stored in JSON format with consistent schema. The data set that we will mainly work on is the review data set, which provides the reviews from users to business; and the business data set, which provides the information of business listed on Yelp. In the reviews data set, we will mainly work with following attributes: business\_id, which is unique for each business listed on Yelp; text, which the review left to this restaurant; and stars, which is the rating left by the reviewer. For the business data set, we will use the business\_id from the reviews data set to match to the reviewed business. Then we can use the information from the business data set to tag and group up business. 

The review data set had over 8 million instances, and it is hard to load all the data at once due the limitation of our computation resource. Therefore, we will utilize the business data set and apply some data mining algorithms to split the data set to reduce the size and avoid the biased data set. Afterward, we will shuffle and split the data set into a 4: 1 train and test partition. For the text part, we will first do the data clean to remove the unnecessary characters and do the contractions for the text. Meanwhile, the vocabularies used in the review are not alway correct. Therefore, we will use the spell corrector library in python to correct the spelling and reduce the vocabulary size. Also, another challenge is raised by the length of each review, which varies from 1 word to a long paragraph. Therefore, we will find a threshold to truncate the long review to increase the efficiency of feature extraction.


\section{Technical Challenge}


\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review.

% include your own bib file like this:
\bibliographystyle{acl}
\bibliography{acl2015}

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

\end{document}